---
title: "OpenML: Connecting R to the Machine Learning Platform OpenML"
subtitle: "whyR? 2018 tutorial -
[https://tiny.cc/whyR2018](https://tiny.cc/whyR2018)"
author: "Giuseppe Casalicchio, Bernd Bischl, Heidi Seibold, Joaquin Vanschoren"
date: "*If you haven't done so yet, create an account on OpenML.org, and install the OpenML R package and either packages farff or RWeka*"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      
---
<!-- For this to work, install xaringan (devtools::install_github('yihui/xaringan')) -->

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(dpi = 300, cache = TRUE, message = FALSE, eval = TRUE)
library(OpenML)
setOMLConfig(confirm.upload = FALSE)
set.seed(123)
```


---
class:inverse

### *Practical*  
<!-- [5 minutes, Joaquin] -->

- Install the OpenML R package (if you haven't done so yet)
- Add your API-key to your config file
- Configure OpenML to your liking


---
class:inverse
### *Practical*  
<!-- [5 minutes, Joaquin] -->
- List all datasets having between 100K and 200K observations and <= 5 features
- List all regression tasks corresponding to data sets having between 50 and 55 observations.
- Find the data.id for dataset 'sonar'
- List all `predictive.accuracy` evaluations for task 39

---
class:inverse
### *Solution*  
- List all datasets having between 100K and 200K observations and <= 5 features
```{r}
datasets = listOMLDataSets(number.of.instances = c(100000, 200000), 
  number.of.features = c(1, 5))
str(datasets, list.len = 10)
```

---
class:inverse
### *Solution*  
- List all regression tasks corresponding to data sets having between 50 and 55 observations.
```{r}
tasks = listOMLTasks(task.type = "Supervised Regression",
  number.of.instances = c(50, 55))
tasks[1:10, 1:5]
```

---
class:inverse
### *Solution*  
- Find the data.id for dataset 'sonar'
```{r}
ds = listOMLDataSets(data.name = "sonar")
str(ds, list.len = 10)
```

---
class:inverse
### *Solution*  
- List all `predictive.accuracy` evaluations for task 39
```{r}
evals = listOMLRunEvaluations(task.id = 39, 
  evaluation.measure = "predictive_accuracy")
str(evals, vec.len = 1)
```

---
class:inverse
### *Practical*  
<!-- [5 minutes, Joaquin] -->
- Download task with task Id 59
- Extract the dataset from this task     
  Hint: read ?OMLTask and look for "input"

---
class:inverse
### *Practical*  
- Download task with task Id 59
```{r}
task = getOMLTask(task.id = 59)
task
```
---
class:inverse
### *Practical*  
- Extract the dataset from this task
```{r}
task$input$data
head(as.data.frame(task))
```


---
class:inverse
### *Practical*  
<!-- [25 minutes, Bernd] -->

- Run your favorite learner/algorithm (from mlr) on task 39 that you already downloaded.
    + Convert the `OMLTask` to an `mlr` task object.
    + Run `listLearners()` to find appropriate learners for that task.
    + Or go to mlr's appendix in the web tutorial to see a table of implemented learners.

- Upload your run to OpenML. Add the tag "whyR2018". Hint: 
```{r, eval=FALSE}
run.id = uploadOMLRun(myrun, tag = "whyR2018")
```

- Check if the upload worked by going to the website. Check if the tag was
  added (you can still add it on the website if you forgot during the upload). 
  
- Check the predictive performance of the run online
(it may take a while before the server has calculated the performance measures $\rightarrow$ give it some time).

---
class:inverse
### *Solution*  

- Run your favorite learner/algorithm (from mlr) on task 39 that you already downloaded.

```{r, warning=FALSE}
# list mlr algos: subset for compact display
mlr.task = convertOMLTaskToMlr(task)
listLearners(mlr.task, warn.missing.packages = FALSE)[1:4, c(1,2,4)] 
# run favorite learner
lrn = makeLearner("classif.rpart", minsplit = 5)
myrun = runTaskMlr(task, lrn)
```

- Upload your run to OpenML. Add the tag "whyR2018". 

```{r, eval=FALSE}
myrun.id = uploadOMLRun(myrun, tags = "whyR2018")
```
```{r, echo=FALSE}
myrun.id = 3829199 # we do not want to upload this every time we generate the slides
```


---
class:inverse
### *Solution*  

- Check if the upload worked by going to the website. Also check if the tag was
  added (you can also still add it on the website). 
  
Use the value from `myrun.id` and go to `r paste0("https://www.openml.org/r/", myrun.id)`.

- Check the predictive performance of the run by looking at several evaluation measures.
- Scroll down to *Evaluation measures*. 

---
class:inverse
### *Solution*  
You can also get the results via
```{r}
str(listOMLRunEvaluations(run.id = myrun.id), list.len = 15)
```

