



---

class:inverse
### *Practical*  
<!-- [25 minutes, Bernd] -->

<!-- TODO: exchange XXX with the task number -->
- Run your favorite learner/algorithm (from mlr) on task XXX that you already downloaded.
Hint: You could run `listLearners(task)` to find appropriate learners for that task.
- Upload your run to OpenML. Add the tag "useR17". 
  Hint: run.id = uploadOMLRun(run.mlr, tag = "useR17")
- Check if the upload worked by going to the website. Also check if the tag was
  added (you can also still add it on the website). 
- Check performance of the run.  Might take a while for server to compute it.

- If you are fast:
    + Run a 2nd learner and compare them on the webpage
    + Add tuning to a learner with an mlr TuneWrapper 
      (much harder, look at the tutorial for this!)

---
class:inverse
### *Practical*  

- Run your favorite learner/algorithm (from mlr) on task XXX that you already downloaded.
Hint: You could run `listLearners(task)` to find appropriate learners for that task.

```{r, eval = myeval, echo = -c(3:4)}
# select the learner manually from lrn.list
lrn.list = listLearners()
# or ask for appropriate learners
appropriate.lrn = 
  listLearners(obj = convertOMLTaskToMlr(task)$mlr.task)
# run favorite learner
lrn = makeLearner("classif.rpart", minsplit = 20))
myrun = runTaskMlr(task, lrn)
```

- Upload your run to OpenML. Add the tag "useR17". 

```{r, eval = myeval}
myrun.id = uploadOMLRun(myrun, tags = "useR17")
myrun.id
```

---
class:inverse
### *Practical*  

- Check if the upload worked by going to the website. Also check if the tag was
  added (you can also still add it on the website). 
  
Use the value from `myrun.id` and go to `r paste0("https://www.openml.org/r/", myrun.id)`.

- Check the predictive performance of the run by looking at several evaluation measures.

   - Go to `r paste0("https://www.openml.org/r/", myrun.id)` 
   - Scroll down to *Evaluation measures*. 

You can also get the results via
```{r, eval = FALSE}
listOMLRunEvaluations(run.id = myrun.id)
```


